---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# r4kc

<!-- badges: start -->
<!-- badges: end -->

The goal of r4kc is to simplify reading and using data posted by Kitsap County in R. 

## Installation

You can install the development version of r4kc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("monkeywithacupcake/r4kc")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(r4kc)
# this will return the three commissioner districts as an sf
commiss <- get_kc_data(get_dataset_name("commission"))
```

You can pull these data down and make a quick map.

```{r}
library(tidyverse)
library(r4kc)
library(sf)

uga <- get_kc_data(get_dataset_name("uga"))
cities_and_uga <- uga %>%
  mutate(type = ifelse(grepl("City ", GMA_JURISDICTION), "City", "UGA")) %>%
  group_by(type, jurisdiction = GMA_JURISDICTION) %>%
  summarize(geometry = st_union(geometry),
            .groups = "drop") %>%
  select(jurisdiction)

ggplot() +
  geom_sf(data = cities_and_uga, aes(fill = jurisdiction)) +
  labs(title = "Cities and UGA in Kitsap County") +
  theme_void()

```


You can do more extensive analysis - combining with census or transit or other kitsap county data. This is especially useful if you want to limit an analysis to a particular area in Kitsap County, for example. 

